\qquad Track4Me is a company which provides three software based services. The services are limited to the citizens of Milan. The given problem is to design and develop a software service called  “Data4Help”,  which acts as an intermediary between the individuals and the other companies. It targets two set of users, individuals and third party. The location and health of the user is extracted from a wearable device. The data from the wearable device is extracted with the help of the API of the wearable device. The software tracks the location and health status of individuals or group of individuals and send the information to the third party on their request to monitor the health of individuals by validating the type of requests. The validation of the requests for the information of specific individuals is done by the individual’s self acceptance or rejection. The requests for the information of group of individuals is decided by Track4Me and generalized by allowing the access to the third party, if the number of individuals whose information is to be accessed is greater than 1000.

\qquad It builds a new service called “AutomatedSOS” over the top of “Data4Help” after monitoring the demand of requests from third parties for giving non-intrusive SOS service to elderly people, which sends the ambulance to individual’s location when the health parameters are below the thresholds. The nearest ambulance is tracked and sent to ensure individual’s quick and efficient recovery. A separate mobile application of Track4Me is to be exclusively developed for the ambulance drivers who are informed by push notifications in the mobile application along with the location and other details of the patient in less than 5 seconds to ensure spontaneity in reaction to emergencies. All the hospitals in Milan are informed to ensure all the ambulance drivers installs TrackMe application.

\qquad A new service called “Track4Run” is built as a source of revenue which allows organizer to organize an event, athletes to participate in the event and spectators to see the athletes position live in a Map. It exploits the service of “Data4Help” which tracks the location of the athletes to be visible to everyone and helps the organizer to monitor the health status of athletes as well. The organize will be registered as an existing or new third-party. The athletes will be registered as existing or new individual and the spectators can be registered as new/existing individual/third party.

\qquad The users can either register as an individual or as an organization/company(third party).Data4Help is a base service which all the individuals and third party will have by default even if the user registers for a different service other than “Data4Help”. The third party can register for two services: “Data4Help” and “Track4Run”. It uses “Data4Help for receiving information about targeted individuals and “Track4Run to organize events for a particular cause/occasion. The third party is a source of revenue for both cases, as Track4Me provides information about individuals and thereby,  provides customers to their organization which brings them profit. Individuals can register for any of the three services. The first service is a free service  with a motive to help them to receive specific input from respective third party for their health issues or other factors. The individual can also upgrade to other services if they are an existing a member using one service by making payment. Payment can be made using PayPal or a credit card. Track4Me guarantees the security of the individuals data and only associates with trusted third party companies. Ultimately, it helps both individuals and third party to manage and monitor their personal data and aims at being a robust and efficient software
