\subsection{Individual}
A person using TrackMe for monitoring his/her vitals using the Data4Help service. He/She gets to register for the service by making an monthly payment and his/her data would be tracked and monitored by the TrackMe.
\subsection{Third Party} 
This can be a person or a company who wish to get the data for the users for some work of his/her concern. They have to register by making a certain payment amount as specified by TrackMe and a valid purpose for the data transfer. The transfer of data is based after proper analysis and validation by the TrackMe.
\subsection{Organizers}
Organizers are those people who use the Track4Run service, who wish to organize an event like a race or a marathon for a cause. They have to register the event with the details of the event, location, date, time and so on. Track4Run is a paid service and hence organizers have to register with a specific cost.
\subsection{Athletes} 
These are those people who join for a specific event organized by mentioning details like name, contact and wearable device to be used and complete the registration by making the payment.
\subsection{Spectators}
These are people who wish to avail the service of Track4Run just to watch the race. He/She can just join to watch a particular race by providing basic details like name, email and the one time payment amount. They can also upgrade their service to watch the upcoming events or receive notifications on upcoming races.
\subsection{Ambulance Drivers}
TrackMe has an application for the Ambulance drivers who gets push notifications from Automated SOS service.  
