\textbf{1. Integration of Data4Help} 
\begin{itemize}
\item Integration of the components of Data4Help of the application server.\newline
-- Request Manager, Individual Details Provider
\item Integration of components of Data4Help with the DBMS. \newline
-- Location Module, Data4Help DB\newline
-- Health Module, Data4Help DB\newline
-- Individuals Details Provider, Data4Help DB
\item Integration of components of Data4Help with the (other) external services. \newline
-- Location Module, Wearable Device API\newline
-- Health Module, Wearable Device API\newline
\end{itemize}
\textbf{2. Integration of Automated SOS}
\begin{itemize}
\item Integration of the components of Automated SOS of the application server.\newline
-- Health Status Controller, Ambulance Details Provider
\item Integration of components of Automated SOS with the DBMS. \newline 
-- Health Status Controller, Data4Help DB
\item Integration of components of Automated SOS with the (other) external services. \newline
-- Ambulance Details Provider, Emergency Services API\newline
-- Ambulance Details Provider, Maps API\newline
\end{itemize}
\textbf{3. Integration of Track4Run}
\begin{itemize}
\item Integration of components of Track4Run with the DBMS. \newline 
-- Event Module, Track4Run DB
\item Integration of components of Track4Run with the (other) external services. \newline
-- Map View Module, Track4Run DB
-- Map View Module, Maps API
\end{itemize}
\textbf{4. Integration of TrackMe}
\begin{itemize}
\item Integration of the components of TrackMe with Data4Help.
\item Integration of components of TrackMe with AutomatedSOS. 
\item Integration of components of TrackMe with Track4Run. 
\item Integration of AutomatedSOS with TrackMe Ambulance Application.
\end{itemize}